The impact of forest management on the temperature sensitivity of organic matter turnover

### 2024-11-12 Manuscript_draft/Draft.Rmd
Minor update on the variance decomposition

## Machine learning variance decomposition: predicting respiration based on edaphic, ecological and enzymatic data

@@

@@

# Appendix
![Posteriors of the scaling parameter, varying as a function of single plots](../Figures/posteriors_boxplots_q10.png){width=60%}

>>>>

## Variance decomposition: predicting respiration based on edaphic, ecological and enzymatic data

@@

## Variance decomposition: predicting Q10 based on edaphic, ecological and enzymatic data

![.](../Figures/mixed_model_relimp.png){width=50%}

![.](../Figures/Q10_PLS_biplot.png){width=50%}

@@

# Appendix
![.](../Figures/posteriors_boxplots_q10.png){width=60%}
